Pillar 1 - Sequential Pattern Mining

### 2019-02-12 Pillar 1 - Sequential Pattern Mining.Rmd

### Courses that were taken before each course
```{r}
d_past_student_course <- d_cumulative_transcript %>%
  select(sequenceID, eventID, item, course_past) %>%
  unnest(item, .drop=F)

>>>>

### Courses that were taken before each course
```{r}
d_transcript_cum_current <- d_transcript_cum %>%
  unnest(
    course_current,
    .drop = FALSE
    )

d_transcript_cum_current %>%
  unnest(
    course_past,
    .drop = FALSE
    )
